\section*{Part C - Practical (50)}

\noindent \begin{center}
\rule[0.5ex]{1\linewidth}{1pt}
\par\end{center}

\begin{comment}
M57.biz is a web start-up company in the United States that is developing a
body art catalogue. The company had $3 million in seed funding and is now
worth about $10 million. It has two founders who are the owners, and 10
additional employees. The current employees are as follows:
     President: Alison Smith
     Chief Financial Ocer: Jean
     Programmers: Bob, Carole, David, and Emmy
     Marketing: Gina and Harris
     BizDev: Indy
M57.biz is a virtual company. The programmers work from their homes and
engage in daily online chat sessions. They have a weekly in-person meeting in
a local office park. Marketing and BizDev are mostly on the road and work
out of their hotel rooms or Starbucks. They have an in-person meeting once
every two week. Most documents that are exchanged in the company are ex-
changed by e-mail. A spreadsheet containing confidential information from
M57.biz was discovered posted on a competitor's website in a technical sup-
port forum, where it was an attachment to a forum post. The spreadsheet was
called M57plan.xlsx". The spreadsheet had originally been created by Jean,
the Chief Financial Officer on her company laptop.
Forensic investigators have interviewed Jean who stated that Alison had
asked her to prepare the spreadsheet as part of a new funding round for the
company, and that Alison had asked her to send the spreadsheet to her by e-
mail. Alison stated that she did not know what Jean was talking about, and
that she had never asked her for the spreadsheet and had never received it by
e-mail. The forensic investigators have forensically imaged the hard drive from
Jean's computer and have provided you the image for forensic examination and
analysis (available via the course page). One of the founders, who have retained
the forensic investigators and you, wants to know the following:
     When did Jean create this spreadsheet?
     How did it get from her computer to the competitor's website?
     Who else from the company is involved?
You are required to conduct a forensic examination of the evidence and prepare
a detailed report of your ndings (fully supported with evidence and technical
explanations). To aid you in your investigations you have been provided with
the following:
     The e-mail address for Alison is Alison@m57.biz and her password is
    ab=8989
     The e-mail address for Jean is jean@m57.biz and her password is gick*1212.
    It is crucial that your report include (along with supporting academic references):
     What digital forensics process model you made use of and motivate why.
     How you would have ensured the legality of your investigation and the
    subsequent admissibility of the digital evidence.
     The application of the scientific method to the investigation
Your report should be 10-15 pages long.
NOTE: While references are likely to be sparse in this document, the 
assessment will focus on the strength of argumentation and justification of your
decision making process. Provide evidence of how you reached your conclusions.

\end{comment}